\documentclass[11pt]{amsart}

\usepackage{a4wide}
\usepackage{paralist}
\usepackage{url}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cS}{\mathcal{S}}

\begin{document}
\begin{center}
\textbf{\sffamily
   Discrete and Algorithmic Geometry }

\medskip
   Julian Pfeifle,
   UPC, 2018
\end{center}

\bigskip

\begin{center}
  \textbf{\sffamily Participants}
\end{center}

\medskip

\section*{Ander Elkoroaristizabal}
(anderelkoro)

I have studied Maths at UPV/EHU, 3 years in Bilbo and a year in UEx. I've focused myself mostly in Abstract Algebra, which I find specially beautiful, and Geometry, of which I enjoy its intuitiveness. I've also used programming to get deeper knowledge of most subjects, so I find it really useful. For the future I would like to find a way of using my taste for Algebra, Geometry and Pure Maths in general in Applied Mathematics.

\medskip

\section*{Víctor Ruiz Herrero}
(rufyzos)

I  have  studied  maths  in  FME,  I  would  like  to  learn  a  lot  of  geometry  in  this course and in the future I would like to be a doctor in Mathematics.

\medskip

\section*{Xavier Gombau Pascual}
(xavi-gombau)

I have studied a degree in Telecommunications Engineering for the last 4 years here in Barcelona, at UPC. This course, I would like to study computation-related topics and code a little bit! I'm not sure what to do in a near future, but I have some ideas as an entrepreneur. Looking forward to enjoy this course! 

\medskip

\section*{Esteve Tarrago Sanchis}
(tarragoesteve)

I  studied computer science and industrial engineering at UPC. There we study some discrete and applied math. I would like to learn more about geometry, and in particular those structures useful to model real-world. One topic that I may focus on the future is reinforcement learning applied on to robots policies. 

\section*{Diego Acedo Moscoso}
(diegoacedo)

I studied a Degree in Mathematics in the University of Cadiz. I am interested mostly in group theory, but I'm also keen on measure theory and algebraic topology, and I do not really dislike many parts of mathematics. I have not learned much geometry before, so I hope with this course I can get some ideas.
I am not sure about my future yet. After finishing this master, I plan to get some job experience, and hopefully some years later I will try to do a Ph.D.

\medskip

\section*{Marta Bustins Molina} 
(MartaBustins) 
I have studied maths in Universitat de Barcelona. I'm more interested in Algebraic Topology, but i do like geometry too. I have done some courses about programming and in this course I would like to learn how to apply it in geometry. In the future I would like to be a doctor in Pure Maths.

\medskip

\section*{Filip Cano Córdoba}
(\texttt{filipcc})

I have studied Maths and Physics Engineering at UPC,
so I have studied mostly the kind of maths that are used in physics.
I've always seen Geometry as a beautiful and mysterious branch of mathematics,
but I have never really felt comfortable in it, so I expect to earn more confidence by
studying this course.  
As for the passions I have for the future, 
my real passion is to be happy. 
In a more concrete way, I would like to pursue a PhD in Mathematics at a European 
university, and I would specially like it to be in Switzerland.
\end{document}


